Online {\IterComp}

### 2017-11-13 abstract.tex
abstract

    Iterative compilation can dramatically improve the performance of a program by searching for the best optimization.
    However, it relies upon repeatedly evaluating optimizations on predefined representative inputs.
    If the developers fail to guess what is a representative input or usage patterns change over time,
    then the wrong optimizations may be selected.
    Searching the optimization space with actual user inputs, during deployment, has previously seemed infeasible.
    Program side effects and difficulties capturing the system state mean that any given input can
    only be executed once. %Since each input may entail a different amount of work, the search cannot use runtime to compare
    %optimizations, and there is no baseline against which to define speedup.
    Unless we find a way to compare optimizations even when inputs are executed only once, we will be unable to use real user
    input for iterative compilation, users will not have the best optimized programs, and performance will suffer.

@@

    Our online iterative compilation method yields programs that get 60\% of the speedup achievable by an offline oracle,
    but without executing any input more than once, which the oracle cannot do.
    Through probe removal we bring the instrumentation overhead down to only 5\% on average, making our
    approach suitable for real-world scenarios. %We show practical online iterative compilation for the first time,
    %optimizing programs according to the range of inputs users actually present.
\end{abstract}

>>>>

    Iterative compilation can dramatically improve the performance of a program by searching for the best optimization. However, it relies
    upon repeatedly evaluating optimizations on predefined representative inputs. If the developers fail to guess what is a representative
    input or usage patterns change over time, then the wrong optimizations may be selected. Searching the optimization space with actual
    user inputs, during deployment, has previously seemed infeasible. Program side effects and difficulties capturing the system state mean
    that any given input can only be executed once, online. Existing performance metrics cannot be used to compare optimizations evaluated
    under different inputs. Unless we devise a new metric that can be used in such a way, we will be unable to apply iterative compilation
    online with real live inputs, users will not have properly optimized programs, and performance will suffer.

@@

    Our online iterative compilation method yields programs that get 60\% of the speedup achievable by an oracle that depends on reusing
    inputs, something that cannot be done online. Through probe removal we bring the instrumentation overhead down to only 5\% on average,
    making our approach suitable for real-world scenarios. %We show practical online iterative compilation for the first time, optimizing
    %programs according to the range of inputs users actually present.
\end{abstract}
